### 2021-08-21 doc/thesis/chapters/implementation.tex
impl done

A testbench is equally important in the HLS implementation, as it is for the VHDL implementation.
The HDL code for the IP is written in \cplusplus\ and thus the testbench is also written in this language.
The execution of the testbench is done in the Xilinx HLS software.
A detailed explanation of how an HLS testbench works in general is given in Chapter~\ref{cha:HLS}.\\

@@

The actual implementation to write the HLS signal data to a file, is implemented as a file-writer \cplusplus\ class within the HLS design code.
These code parts are only evaluated during simulation, which is achieved by using pre-processor defines.
The following code shows an example of this file-writer class.\\

@@

The testbench is especially designed around the \textit{Design For Reuse} segment of the SIMILAR concept, which is introduced in Section~\ref{sec:SimilarProcess}.
This is the case because of two major parts.
%It is not only using the exact same Python code for analysis, but is also using parts of the application software code directly, to load the testbench input data.\\

@@

\includepicture [0.8] [0] [H] {Overview of the testbench and the reuse of the application software. The HLS IP is displayed with dotted lines, to point out that it is the same in testbench and hardware.} {testbench_hls_overview_reuse} {img/draw.io/testbench_hls_overview_reuse}

@@

The streams use the types \texttt{iq\_sample\_t} and \texttt{audio\_sample\_t}, which are structs of two 16-bit fixed point variables and thus represent a width of 32 bit.
The configuration and status registers are also implemented as structs, that contain multiple variables to represent the separate registers.
For the registers, a special detail is the distinction between the register types read-write and read-only.
This difference is made by using a value-by-reference or a pointer value, for configuration and status interface, respectively.
Consequently, the configuration registers become read-writeable and the status registers remain read-only.\\

The \texttt{bundle} keyword in the pragma-directives combine the two register groups into a single AXI4-Lite bus interface, instead of creating one bus each.
This may be of advantage in the application software later, since it only needs to handle a single base address.
The interface for the LEDs that can be connected is implemented as a data-only type, which does not have any protocol assigned.
It simply represents the data value that is written to the \cplusplus\ variable.
The usage of a data type with variable bitwidth, such as \texttt{ap\_int} in the example, is of advantage since only the actually required number of connections is implemented in the interface.

@@

In the VHDL implementation, this is implemented with a counter that counts the number of incoming samples.
If the counter reaches the number that matches the downsampling rate, is forwards the current sample.
Otherwise, the incoming samples are discarded.\\

>>>>

A testbench is equally important in the HLS implementation, as it is for the VHDL implementation.
The HDL code for the IP is written in \cplusplus\ and thus, the testbench is also written in this language.
The execution of the testbench is done in the Xilinx Vivado HLS software.
A detailed explanation of how an HLS testbench works in general is given in Chapter~\ref{cha:HLS}.\\

@@

The actual implementation to write the HLS signal data to a file, is implemented as a file-writer \cplusplus\ class within the HLS design code.
These code parts are only compiled for simulation, which is achieved by using pre-processor defines.
The following code shows an example of the usage of this file-writer class.\\

@@

The testbench is especially designed around the \textit{Design For Reuse} segment of the \mbox{SIMILAR} concept, which is introduced in Section~\ref{sec:SimilarProcess}.
This is the case because of two major parts.
%It is not only using the exact same Python code for analysis, but is also using parts of the application software code directly, to load the testbench input data.\\

@@

\includepicture [0.8] [0] [H] {Overview of the testbench and the reuse of the application software in testbench and hardware. The HLS IP is displayed with dotted lines, to point out that it is the same in testbench and hardware.} {testbench_hls_overview_reuse} {img/draw.io/testbench_hls_overview_reuse}

@@

The streams use the types \texttt{iq\_sample\_t} and \texttt{audio\_sample\_t}, which are structs of two 16-bit fixed point variables and thus represent a width of 32 bit.
The configuration- and status registers are also implemented as structs, that contain multiple variables to represent the separate registers.
For the registers, a special detail is the distinction between the register types read-write and read-only.
This difference is made by using a value-by-reference or a pointer value, for configuration and status interface, respectively.
Consequently, the configuration registers become read-writeable and the status registers remain read-only.\\

The \texttt{bundle} keyword in the pragma-directives combine the two register groups into a single AXI4-Lite bus interface, instead of creating one bus each.
This is of advantage in the application software later, since it only needs to handle a single base address.
The interface for the LEDs that can be connected, is implemented as a data-only type, which does not have any protocol assigned.
It simply represents the data value that is written to the \cplusplus\ variable.
The usage of a data type with variable bitwidth, such as \texttt{ap\_int} in the example, is of advantage since only the actually required number of connections is implemented in the interface.

@@

In the VHDL implementation, this is implemented with a counter that counts the number of incoming samples.
If the counter reaches the number that matches the downsampling rate, it forwards the current sample.
Otherwise, the incoming samples are discarded.\\
